Supplementary 1 - Considering scale in multilayer animal social networks

### 2020-06-18 paper/manuscript.Rmd
fix encoding in rmd

---
title: Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   bookdown::github_document2: default
   bookdown::word_document2:
     reference_docx: template.docx
knit: (function(inputFile) {
  rmarkdown::render(inputFile, output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

source('../scripts/00-variables.R')

>>>>

---
title: Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   bookdown::github_document2: default
   # bookdown::word_document2:
   #   reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

@@

# source('../scripts/00-variables.R')

### 2020-06-18 paper/supplement.Rmd
rm source bc of self invalidation
fix encoding in rmd

---
title: Supplementary 1 - Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   bookdown::github_document2: default
   # bookdown::word_document2:
   #   reference_docx: template.docx
knit: (function(inputFile) {
  rmarkdown::render(inputFile,
  output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---

>>>>

---
title: Supplementary 1 - Considering scale in multilayer animal social networks
author: Alec L. Robitaille^1\*^, Quinn M.R. Webber^2^, Julie W. Turner^1^, Eric Vander Wal^1,2^
date: |
  | ^1^Department of Biology, Memorial University of Newfoundland, Canada
  | ^2^Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
  | \*Corresponding author: Alec L. Robitaille (robit.alec@gmail.com)
output:
   bookdown::github_document2: default
   # bookdown::word_document2:
   #   reference_docx: template.docx
knit: (function(inputFile, encoding) {
  rmarkdown::render(input = inputFile, encoding = encoding, output_format = "all") })
bibliography: ../references/knitcite.bib
csl: csl.csl
---
